\vspace{-0.25em}\thetitle

### 2009-07-21 paper.tex
...

The fundamental concept underlying this work is \emph{linear representation of network traffic}~\cite{Karpinski08}.
A linear representation is a function that maps sets of flows to vectors, the coordinates of which describe aspects of flow behavior;
the representation must also satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
An entire traffic trace may be represented as a matrix whose rows are the representations of flows in the trace.
We restrict our consideration to a particularly natural and powerful class of representations whose coordinates describe the frequencies of flow features.
For example, the representation can have a dimension for each packet size up to 1500; coordinates in these dimensions indicate the number of packets of each size.
Port numbers, \caps{IP} protocol type, and inter-packet intervals can be handled similarly.
% Examples of flow features are the number of packets of a certain size or the use of a particular port number.
% The fundamental premise of this work, and of the sequel, is that the representatives of actual flow behaviors can be understood as being sampled from

The essential observation of this research is that under such representations, real flows lie near the union of a small set of low rank subspaces.
This property allows us to perform a drastic model reduction on trace traffic patterns while preserving most characteristics of the original traffic.
Moreover, when observable characteristics of flows are separated from features to be predicted, this model reduction is similar to a classical linear regression:
it allows us to use a least squares optimization on observed features to predict behavior.
We use this technique to predict the following characteristics of each flow from observing only a handful of its initial packets:
\begin{enumerate}
  \item the distribution of packets sizes,
  \item the distribution of inter-packet intervals,
  \item the number of packets that will be in the flow.
\end{enumerate}
From these properties we can indirectly predict many other properties, including the total duration and data volume.

>>>>

The fundamental concept underlying this work is \emph{linear representation of network traffic}~\cite{Karpinski08}.
A linear representation is a function that maps sets of flows to vectors, the coordinates of which describe aspects of flow behavior;
it must distribute additively over set unions.
% the representation must also satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
An entire traffic trace may be represented as a matrix whose rows are the representations of flows in the trace.
We restrict our consideration to a particularly natural and powerful class of representations whose coordinates are the frequencies of flow features in a set of flows.
For example, the representation can have a dimension for each packet size up to 1500; coordinates in these dimensions indicate the number of packets of each size.
Port numbers, \caps{IP} protocol type, and inter-packet intervals can be handled similarly.
% Examples of flow features are the number of packets of a certain size or the use of a particular port number.
% The fundamental premise of this work, and of the sequel, is that the representatives of actual flow behaviors can be understood as being sampled from

The essential observation of this research is that under such representations, real flows lie near the union of a small set of low-rank subspaces.
This property allows us to perform a drastic model reduction on trace traffic patterns while preserving the essential characteristics of the original traffic.
Moreover, when observable characteristics of flows are separated from features to be predicted, this model reduction is similar to a classical linear regression:
it allows us to use a least squares optimization on observed features to predict behavior.
We use this technique to predict the following characteristics of each flow from observing only a handful of its initial packets:
\begin{enumerate}
  \item the distribution of packets sizes,
  \item the distribution of inter-packet intervals,
  \item the number of packets that will be in the flow.
\end{enumerate}
From these properties we can indirectly predict many other properties, including the total duration and data volume.
